Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-07 Papers/ms.tex
More caption work

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens2.pdf}
\caption{{\revisions
Same as Figure~\ref{fig:N_lens1}, but for the `harder' simulated dataset.
}
\label{fig:N_lens2}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures2.pdf}
\caption{{\revisions
Same as Figure~\ref{fig:substructures1}, but for the `harder' simulated dataset.
The true number of substructures was 10, which also happens to be the posterior
mode. Only five substructures were located within the domain of the image, but
$N_{\rm lens} = 10$ is probable because the spread-out positions of the
m
}
\label{fig:substructures2}}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens2.pdf}
\caption{{\revisions
Same as Figure~\ref{fig:N_lens1}, but for the `harder' simulated dataset.
The true number of substructures was 10, which also happens to be the posterior
mode. Only five substructures were located within the domain of the image, but
$N_{\rm lens} = 10$ is probable because the spread-out positions of the
substructures imply that $R_{\rm lens}$ is probably large.
}
\label{fig:N_lens2}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures2.pdf}
\caption{{\revisions
Same as Figure~\ref{fig:substructures1}, but for the `harder' simulated dataset.
For all of the substructures located close to the ring, the positions were well
constrained. There was weak evidence for some substructures that did not in
fact exist.
}
\label{fig:substructures2}}
\end{center}
\end{figure}
